*Supplementary Material*

### 2022-02-18 ms/manuscript.Rmd
Add monophyly table

@@

# Targets from MS workflow
tar_load(
	c(
		accepted_species,
		sanger_sampling,
		coverage_by_rank,
		total_coverage,
		bb_coverage_by_rank,
		bb_total_coverage,
		gb_species_by_year,
		ref_files,
		other_dates,
		crown_ages,
		fossil_ferns_raw,
		family_stem_ages
	),
	store = here::here("_targets")
)
```

@@

```{r topology-stats}
ferns_bs <- get_bs(plastome_tree, c("Equisetum_arvense", "Danaea_nodosa"))
hym_gle_bs <- get_bs(plastome_tree, c("Dipteris_conjugata", "Hymenophyllum_polyanthos"))
cyath_salv_bs <- get_bs(plastome_tree, c("Plagiogyria_adnata", "Azolla_filiculoides"))
denn_poly_bs <- get_bs(plastome_tree, c("Dennstaedtia_hirsuta", "Pseudophegopteris_aurita"))
```

@@

@@

```{r plot-prep}
## ---- plot-prep-main

@@

# Make tibble for annotating major clades
clade_tibble <- 
	# Use assess_monophy to get MRCA of each major clade
	# They should all by monophyletic anyways
	select(sanger_sampling, species, major_clade) %>%
	assess_monophy(
		taxon_sampling = .,
		tree = plastid_tree_dated,
		tax_levels = "major_clade"
	) %>%
	get_result_monophy(1) %>%
	# Exclude lycophytes
	filter(!taxon %in% c(
		"Selaginellales", "Lycopodiales", "Isoëtales", "Isoetales")) %>%
	verify(all(monophyly == "Yes")) %>%
	transmute(major_clade = taxon, mrca = parse_number(mrca)) %>%
	left_join(clade_cols_tib, by = "major_clade")
```

>>>>

```{r formatters-load}
# Load formatting functions defined in functions.R
knitr::read_chunk(
	here::here("R/functions.R"),
	labels = "formatters",
	from = "formatters start",
	to = "formatters end"
)
```

```{r, formatters}
```

@@

# Targets from MS workflow
tar_load(
	c(
		accepted_species,
		sanger_sampling,
		coverage_by_rank,
		total_coverage,
		bb_coverage_by_rank,
		bb_total_coverage,
		gb_species_by_year,
		ref_files,
		other_dates,
		crown_ages,
		fossil_ferns_raw,
		family_stem_ages,
		fern_monophy_summ_tbl
	),
	store = here::here("_targets")
)
```

@@

```{r topology-stats}
ferns_bs <- get_bs(plastome_tree, c("Equisetum_arvense", "Danaea_nodosa"))
hym_gle_bs <- get_bs(plastome_tree, c("Dipteris_conjugata", "Hymenophyllum_polyanthos"))
cyath_salv_bs <- get_bs(plastome_tree, c("Plagiogyria_adnata", "Azolla_filiculoides"))
denn_poly_bs <- get_bs(plastome_tree, c("Dennstaedtia_hirsuta", "Pseudophegopteris_aurita"))

fern_monophy_summ <-
fern_monophy_summ_tbl %>%
	mutate(
		n = as.integer(n),
		p = percent(percent)
	) %>%
	split(.$tax_level) %>%
	map(~split(., .$monophyly))
```

@@

All sampled orders, suborders, families, and subfamilies were recovered as monophyletic (or monotypic) with the exception of Polypodioideae, which is known to be paraphyletic relative to Grammitidoideae [@PteridophytePhylogenyGroupI2016].
`r fern_monophy_summ$genus$No$n` genera (`r fern_monophy_summ$genus$No$p`) were non-monophyletic (`r s_table("monophy")`).

@@

```{r plot-prep}
### plot-prep start

@@

# Make tibble for annotating major clades
clade_tibble <- 
	# Use assess_monophy to get MRCA of each major clade
	# They should all by monophyletic anyways
	select(sanger_sampling, species, major_clade) %>%
	assess_monophy(
		taxon_sampling = .,
		tree = plastid_tree_dated,
		tax_levels = "major_clade"
	) %>%
	get_result_monophy(1) %>%
	# Exclude lycophytes
	filter(!taxon %in% c(
		"Selaginellales", "Lycopodiales", "Isoëtales", "Isoetales")) %>%
	verify(all(monophyly == "Yes")) %>%
	transmute(major_clade = taxon, mrca = parse_number(mrca)) %>%
	left_join(clade_cols_tib, by = "major_clade")
### plot-prep end
```

### 2022-02-18 ms/si.Rmd
Add monophyly table

@@

tar_load(
	c(
		sanger_alignment_tbl,
		sanger_sampling,
		sanger_accessions_selection,
		plastome_tree,
		plastid_tree_dated,
		fossil_calibration_tips,
		ppgi_taxonomy),
	store = ftol_cache
)

# Targets from MS workflow
tar_load(
	c(
		accepted_species,
		gb_species_by_year,
		ref_files,
		other_dates,
		du_dates_all,
		family_stem_ages,
		fossil_ferns_raw,
		pteridocat_ppgi_diff_refs_out,
		pteridocat_ppgi_diff_notes
	),
	store = here::here("_targets")
)
```

@@

```{r plot-prep-load}
# Load the plot prep code from the main MS
knitr::read_chunk(
	here::here("ms/manuscript.Rmd"),
	labels = "plot-prep-main",
	from = "og_taxa <-",
	to = "left_join\\(clade_cols_tib"
)
```

>>>>

```{r formatters-load-si}
# Load formatting functions defined in functions.R
knitr::read_chunk(
	here::here("R/functions.R"),
	labels = "formatters-si",
	from = "formatters start",
	to = "formatters end"
)
```

```{r, formatters-si}
```

@@

tar_load(
	c(
		sanger_alignment_tbl,
		sanger_sampling,
		sanger_accessions_selection,
		plastome_tree,
		plastid_tree_dated,
		fossil_calibration_tips,
		ppgi_taxonomy,
		monophy_by_clade),
	store = ftol_cache
)

# Targets from MS workflow
tar_load(
	c(
		accepted_species,
		gb_species_by_year,
		ref_files,
		other_dates,
		du_dates_all,
		family_stem_ages,
		fossil_ferns_raw,
		pteridocat_ppgi_diff_refs_out,
		pteridocat_ppgi_diff_notes,
		fern_monophy_summ_tbl
	),
	store = here::here("_targets")
)
```

@@

```{r monophy, results = "markup"}
fern_monophy_summ_tbl %>%
	mutate(
		tax_level = str_to_sentence(tax_level),
		percent = percent(percent, accuracy = 0.1) %>%
			str_replace_all("100\\.0", "100")) %>%
	select(
		`Taxonomic level` = tax_level, Monophyly = monophyly,
		n, `%` = percent) %>%
	flextable() %>%
	italic(1,3, part = "header") %>%
	autofit()
```

**`r s_table("monophy")`**.
Monophyly by taxonomic level for ferns in FTOL.

```{r plot-prep-load}
# Load the plot prep code from the main MS
knitr::read_chunk(
	here::here("ms/manuscript.Rmd"),
	labels = "plot-prep-main",
	from = "plot-prep start",
	to = "plot-prep end"
)
```
